More than one Author with different Affiliations

### 2012-04-22 paper/ms.tex
Toy model specification
Fixed convolution formula

@@

\appendix
\section{Pixel Convolved PSF}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image gives rise to the observed data. First, it is convolved with a
PSF $g(x, y)$ (assumed normalised to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x, y) &=& \iint f_0(x, y)g(x - \delta_x, y - \delta_y)
\, d\delta_x \, d\delta_y
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation, such that
the true flux $F$ within a particular pixel is:
\begin{eqnarray}
F_{\rm{pixel}} &=& \iint_{\rm{pixel}} f_{\rm blurred}(x, y) \,dx\,dy
\end{eqnarray}

>>>>

\subsection{Toy Model}
For the first implementation I wrote at NYU, I used the following model and
priors:
\begin{itemize}
\item $N \sim \textnormal{Uniform}(0, 1, 2, ..., 1000)$ \\
\item The parameters of the spatial
distribution: $\alpha = \left\{x_c, y_c, \sigma\right\}$ \\
\item The spatial distribution: $p(x_i, y_i | \alpha)\sim\mathcal{N}\left(
\texttt{mean}=(x_c, y_c), \texttt{covariance}=
\left(\begin{array}{cc}\sigma^2 & 0 \\ 0 & \sigma^2\end{array}\right)\right)$ \\
\item The luminosity function: $p(f_i | \beta) \sim
\textnormal{Exponential}\left(\texttt{mean}=\beta\right)$
\end{itemize}

@@

\appendix
\section{Pixel Convolved PSF}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image gives rise to the observed data. First, it is convolved with a
PSF $g(x, y)$ (assumed normalised to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x, y) &=& \iint f_0(x-\delta_x, y-\delta_y)
g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \label{blur}
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation, such that
the true flux $F$ within a particular pixel is:
\begin{eqnarray}
F_{\rm{pixel}} &=& \iint_{\rm{pixel}} f_{\rm blurred}(x, y) \,dx\,dy
\label{pixel}
\end{eqnarray}
We observe $F_{\rm{pixel}}$ for many pixels, with noise added.

Combining Equations~\ref{blur} and~\ref{pixel} gives:
\begin{eqnarray}
F_{\rm{pixel}} &=& \iint_{\rm{pixel}} \iint f_0(x-\delta_x, y-\delta_y)
g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \,dx\,dy
\end{eqnarray}
